---
title: "A Text Mining on customer reviews of the 3 biggest airlines"
output: html_notebook
---
We decide to take a look inside customer reviews of the 3 biggest airlines to confirm the rating of customers. By using sentiment analysis, we can answer the question which airline receive worst reviews from customers and which aspects they will need to improve for better. 

```{r}
aa <- read.csv('AA.csv', header = TRUE, stringsAsFactors = FALSE)
aa <- aa[, !names(aa) %in% c('X')]
head(aa)
lufthansa <- read.csv('Lufthansa.csv', header = TRUE, stringsAsFactors = FALSE)
lufthansa <- lufthansa[, !names(lufthansa) %in% c('X')]
head(lufthansa)
csa <- read.csv('China_Southern_Airlines.csv', header = TRUE, stringsAsFactors = FALSE)
csa <- csa[, !names(csa) %in% c('X')]
head(csa)
```

```{r}
library(ggplot2)
ggplot(aa, aes(class, ratings)) + geom_col(aes(fill=class))
```

Most airlines receive reviews from customers riding Economy. AA has more reviews of customers riding First Class than Business Class.

```{r}
aa$ratings_ <- aa$ratings 
aa$ratings_ <- gsub('[1-3]', 'negative', aa$ratings_)
aa$ratings_ <- gsub('[4-5]', 'positive', aa$ratings_)
aa
```

```{r}
aa$class_ <- aa$class
aa$class_ <- gsub('Premium Economy', 'High Price', aa$class_)
aa$class_ <- gsub('First Class', 'High Price', aa$class_)
aa$class_ <- gsub('Business Class', 'High Price', aa$class_)

aa$class_ <- gsub('Economy' , 'Normal Price', aa$class_)
aa
```

```{r}
#lapply(aa$number_of_reviews_, function(x) {if (x <= 50) {replace(aa$number_of_reviews_, x, 'newbie')} else {replace(aa$number_of_reviews_, x, 'regular')}}) 
#replace(aa$number_of_reviews_, aa$number_of_reviews_ %in% c(1:50), 'newbie')
aa$number_of_reviews_ <- aa$number_of_reviews
aa$number_of_reviews_ <- as.numeric(gsub(",", "", aa$number_of_reviews_))
aa$number_of_reviews_[aa$number_of_reviews_ %in% c(1:50)] <- 'newbie'
aa$number_of_reviews_[aa$number_of_reviews_ %in% c(51:500000)] <- 'regular'
aa
```

```{r}
aa$ratings_ <- as.factor(aa$ratings_)
aa$ratings_ <- relevel(aa$ratings_, 'negative')
aa$class_ <- as.factor(aa$class_)
aa$class_ <- relevel(aa$class_, 'Normal Price')

```



```{r}
str(aa)
```


```{r}
model1 <- glm(ratings_ ~ class_, aa, family = binomial())
model1
```

```{r}
summary(model1)
```

Lower values of −2LL indicate that the model is predicting the outcome variable more accurately.

The crucial statistic is the z-statistic which has a normal distribution and tells us whether the b coefficient for that predictor is significantly different from zero. If the coefficient is significantly different from zero then we can assume that the predictor is making a significant contribution to the prediction of the outcome (Y).

```{r}
modelChi <- model1$null.deviance - model1$deviance # subtracting the deviance from the null deviance
chidf <- model1$df.null - model1$df.residual # which is 1
chisq.prob <- 1 - pchisq(modelChi, 1)
chisq.prob
```

Because this probability is less than .05, we can reject the null hypothesis that the model is not better than chance at predicting the outcome. We can report that including High Price produced a significant improvement in the fit of the model, p = 0.0015.
We could say that Intervention was a significant predictor of positive reviews, z = 3.139, p < .002.



```{r}
<<<<<<< HEAD
library(broom)
=======
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
augmented_mod <- augment(model1)
glimpse(augmented_mod)
```

```{r}
<<<<<<< HEAD
graph_data <- ggplot(aa, aes(class_, ratings_))
graph_data + geom_jitter(width=0, height=0.05, alpha = .5) +
  geom_smooth(method = 'glm', se=FALSE)
=======
graph_data <- ggplot(aa, aes(class, number_of_reviews))
graph_data + geom_point() + geom_smooth(method = 'glm')
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
```


```{r}
sum(is.numeric(aa$number_of_reviews_))
```



```{r}
aa$number_of_reviews_ <- as.factor(aa$number_of_reviews_)
aa$number_of_reviews_ <- relevel(aa$number_of_reviews_, 'regular')
model2 <- glm(ratings_ ~ class_ + number_of_reviews_, aa, family = binomial())
model2
```


```{r}
library(qdap); library(tm); library(tidytext); library(dplyr)
```


```{r}
#lufthansa[lufthansa$ratings == 1 or lufthansa$ratings == 2, 'ratings']
#num_neg_luft <- sum(lufthansa$ratings %in% c(1, 2))
#num_neg_luft
cat("Proportion of negative reviews of Lufthansa:", sum(lufthansa$ratings %in% c(1, 2, 3))/length(lufthansa$ratings), '\n')
cat("Proportion of positive reviews of Lufthansa:", sum(lufthansa$ratings %in% c(4, 5))/length(lufthansa$ratings), '\n')

cat("Proportion of negative reviews of AA:", sum(aa$ratings %in% c(1, 2, 3))/length(aa$ratings), '\n')
cat("Proportion of positive reviews of AA:", sum(aa$ratings %in% c(4, 5))/length(aa$ratings), '\n')

cat("Proportion of negative reviews of CSA:", sum(csa$ratings %in% c(1, 2, 3))/length(lufthansa$ratings), '\n')
cat("Proportion of positive reviews of CSA:", sum(csa$ratings %in% c(4, 5))/length(csa$ratings), '\n')

```


```{r}
proportion = matrix(c(c(0.4038095, 0.5961905), c(0.5085714, 0.4914286), c(0.4057143, 0.5942857)), nrow = 3, byrow = TRUE)
proportion_df <- as.data.frame(proportion)
rownames(proportion_df) = c("Lufthansa", "AA", "China Southern")
colnames(proportion_df) = c('neg', 'pos')
proportion_df
```

```{r}
airline <- c(rep("Lufthansa", 2), rep("AA", 2), rep("China Southern", 2))
Value <- c(0.4038095, 0.5961905, 0.5085714, 0.4914286, 0.4057143, 0.5942857)
sentiment <- c(rep(c("neg", "pos"), 3))
proportion_df_long <- data.frame(Value, sentiment, airline)
proportion_df_long
```

```{r}
library(ggplot2)
ggplot(proportion_df_long, aes(x = airline, y = Value)) +
  geom_col(position = "stack", aes(fill=sentiment)) + 
  scale_fill_manual(values = c("red", "blue"))
```

```{r}
library(qdap)
library(stringi)
# AA
aa$reviews <- stri_encode(aa$reviews, "", "UTF-8")
aa_pol <- polarity(aa$reviews)
aa_pol$all
summary(aa_pol$all$polarity)
# Lufthansa
lufthansa$reviews <- stri_encode(lufthansa$reviews, "", "UTF-8")
lufthansa_pol <- polarity(lufthansa$reviews)
lufthansa_pol$all
summary(lufthansa_pol$all$polarity)
# CSA
csa$reviews <- stri_encode(csa$reviews, "", "UTF-8")
csa_pol <- polarity(csa$reviews)
csa_pol$all
summary(csa_pol$all$polarity)
```


```{r}
all_df <- data.frame(polarity = c(aa_pol$all$polarity, lufthansa_pol$all$polarity, csa_pol$all$polarity),
                     airline = c(rep("AA", dim(aa)[1]), rep("Lufthansa", dim(lufthansa)[1]),
                                 rep("CSA", dim(csa)[1])))
all_df
```

```{r}
library(RColorBrewer)
ggplot(all_df, aes(x = polarity, y = ..density..)) +
  geom_histogram(color = "grey60") +
  geom_density(aes(fill = airline), size = 0.75) +
  facet_wrap( ~ airline) +
  scale_color_manual()
  #scale_color_brewer(palette = "YlOrRd")
```

As predicted, polarity scores on American Airline has a positive skew. This mean American Airline receives more negative feedback from their customers.

```{r}
<<<<<<< HEAD
library(dplyr)
=======
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
aa <- read.csv('AA.csv', header = TRUE, stringsAsFactors = FALSE)
lufthansa <- read.csv('Lufthansa.csv', header = TRUE, stringsAsFactors = FALSE)
csa <- read.csv('China_Southern_Airlines.csv', header = TRUE, stringsAsFactors = FALSE)

names(aa)[names(aa) == "X"] <- "ID"
names(lufthansa)[names(lufthansa) == "X"] <- "ID"
names(csa)[names(csa) == "X"] <- "ID"

tidy_aa <- aa %>%
  unnest_tokens(word, reviews) %>%
  group_by(ID) %>%
  mutate(original_word_order = seq_along(word)) %>%
  anti_join(stop_words) %>%
  mutate(airline = c(rep("AA"))) %>%
<<<<<<< HEAD
  dplyr::select(ID, word, original_word_order, airline)
=======
  select(ID, word, original_word_order, airline)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4

tidy_luft <- lufthansa %>%
  unnest_tokens(word, reviews) %>%
  group_by(ID) %>%
  mutate(original_word_order = seq_along(word)) %>%
  anti_join(stop_words) %>%
  mutate(airline = c(rep("Lufthansa"))) %>%
<<<<<<< HEAD
  dplyr::select(ID, word, original_word_order, airline)
=======
  select(ID, word, original_word_order, airline)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4

tidy_csa <- csa %>%
  unnest_tokens(word, reviews) %>%
  group_by(ID) %>%
  mutate(original_word_order = seq_along(word)) %>%
  anti_join(stop_words) %>%
  mutate(airline = c(rep("CSA"))) %>%
<<<<<<< HEAD
  dplyr::select(ID, word, original_word_order, airline)
=======
  select(ID, word, original_word_order, airline)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
  
```


```{r}
<<<<<<< HEAD
tidy_csa
```


```{r}
=======
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
pos_neg_aa <- tidy_aa %>%
  inner_join(get_sentiments('bing')) %>%
  count(sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(polarity = positive - negative, airline = c(rep("AA")))

pos_neg_luft<- tidy_luft %>%
  inner_join(get_sentiments('bing')) %>%
  count(sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(polarity = positive - negative, airline = c(rep("Lufthansa")))

<<<<<<< HEAD
pos_neg_csa <- tidy_csa %>%
=======
pos_neg_csa <- tidy_luft %>%
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
  inner_join(get_sentiments('bing')) %>%
  count(sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(polarity = positive - negative, airline = c(rep("CSA")))

all_pos_neg <- merge(merge(pos_neg_aa, pos_neg_luft , all = TRUE), pos_neg_csa, all = TRUE)
all_pos_neg
```


```{r}
<<<<<<< HEAD
library(RColorBrewer)
=======
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
ggplot(all_pos_neg, aes(x = airline, y = polarity)) +
  geom_boxplot(fill = c("#bada55", "#F00B42", "#F001ED"), col = "darkred") + 
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 0.02) +
  theme_gdocs() +
  ggtitle("Airline Polarity")
```


<<<<<<< HEAD
- From all above methods, we conclude that China Southern and Lufthansa have been receiving better reviews than American Airline.
- Distribution of Polarity score on Lufthansa reviews is almost normal with an outlier at -8.
- CSA distribution is skwed to the left
=======
From all above methods, we conclude that China Southern and Lufthansa have been receiving better reviews than American Airline.
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4

Write functions to clean texts of reviews

```{r}
# qdap cleaning function
qdap_clean <- function(x) {
  x <- replace_abbreviation(x)
  x <- replace_contraction(x)
  x <- replace_symbol(x)
  x <- tolower(x)
  return(x)
}

# tm cleaning function
tm_clean <- function(corpus) { 
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "american airlines", "lufthansa", "china southern airlines",  "china southern")) 
  return(corpus) 
}
```

Extract positive and negative reviews from each airline

```{r}
aa_pos <- aa %>%
  filter(ratings == c(4, 5)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(aa_pos)

aa_neg <- aa %>%
  filter(ratings == c(1, 2)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(aa_neg)

luft_pos <- lufthansa %>%
  filter(ratings == c(4, 5)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(luft_pos)

luft_neg <- lufthansa %>%
  filter(ratings == c(1, 2)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(luft_neg)

csa_pos <- csa %>%
  filter(ratings == c(4, 5)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(csa_pos)

csa_neg <- csa %>%
  filter(ratings == c(1, 2)) %>%
<<<<<<< HEAD
  dplyr::select(reviews)
=======
  select(reviews)
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
head(csa_neg)
```

Apply the qdap_clean and tm_clean functions

```{r}
# Clean text with qdap_clean function
qdap_clean_aa_pos <- qdap_clean(aa_pos)
qdap_clean_aa_neg <- qdap_clean(aa_neg)

qdap_clean_luft_pos <- qdap_clean(luft_pos)
qdap_clean_luft_neg <- qdap_clean(luft_neg)

qdap_clean_csa_pos <- qdap_clean(csa_pos)
qdap_clean_csa_neg <- qdap_clean(csa_neg)

# Source and create a corpus
aa_pos_corp <- VCorpus(VectorSource(qdap_clean_aa_pos))
aa_neg_corp <- VCorpus(VectorSource(qdap_clean_aa_neg))

luft_pos_corp <- VCorpus(VectorSource(qdap_clean_luft_pos))
luft_neg_corp <- VCorpus(VectorSource(qdap_clean_luft_neg))

csa_pos_corp <- VCorpus(VectorSource(qdap_clean_csa_pos))
csa_neg_corp <- VCorpus(VectorSource(qdap_clean_csa_neg))

# tm_clean the corpus
aa_p_corp <- tm_clean(aa_pos_corp)
aa_n_corp <- tm_clean(aa_neg_corp)

luft_p_corp <- tm_clean(luft_pos_corp)
luft_n_corp <- tm_clean(luft_neg_corp)

csa_p_corp <- tm_clean(csa_pos_corp)
csa_n_corp <- tm_clean(csa_neg_corp)
```


```{r}
library(RWeka)
tokenizer <- function(x) {
  NGramTokenizer(x, Weka_control(min = 2, max = 2))
}

# Create term-document-matrix
aa_p_tdm <- TermDocumentMatrix(aa_p_corp, control = list(tokenize=tokenizer))
aa_n_tdm <- TermDocumentMatrix(aa_n_corp, control = list(tokenize=tokenizer))

luft_p_tdm <- TermDocumentMatrix(luft_p_corp, control = list(tokenize=tokenizer))
luft_n_tdm <- TermDocumentMatrix(luft_n_corp, control = list(tokenize=tokenizer))

csa_p_tdm <- TermDocumentMatrix(csa_p_corp, control = list(tokenize=tokenizer))
csa_n_tdm <- TermDocumentMatrix(csa_n_corp, control = list(tokenize=tokenizer))

```


```{r}
# Create tdm matrix
aa_p_tdm_m <- as.matrix(aa_p_tdm)
aa_n_tdm_m <- as.matrix(aa_n_tdm)

luft_p_tdm_m <- as.matrix(luft_p_tdm)
luft_n_tdm_m <- as.matrix(luft_n_tdm)

csa_p_tdm_m <- as.matrix(csa_p_tdm)
csa_n_tdm_m <- as.matrix(csa_n_tdm)

# Create frequency
aa_p_freq <- rowSums(aa_p_tdm_m)
aa_n_freq <- rowSums(aa_n_tdm_m)

luft_p_freq <- rowSums(luft_p_tdm_m)
luft_n_freq <- rowSums(luft_n_tdm_m)

csa_p_freq <- rowSums(csa_p_tdm_m)
csa_n_freq <- rowSums(csa_n_tdm_m)
```


```{r}
library(wordcloud)
wordcloud(names(aa_n_freq), aa_n_freq, max.words = 100, color='red')
 
```


```{r}
wordcloud(names(luft_p_freq), luft_p_freq, max.words = 100, color='blue')
```

Plot the 10 most common words in positive reviews of China Souther Airlines

```{r}
# Calculate the row sums of coffee_m
term_frequency <- rowSums(csa_p_tdm_m)

# Sort term_frequency in decreasing order
term_frequency <- sort(term_frequency, decreasing = TRUE)

# Plot a barchart of the 10 most common words
barplot(term_frequency[1:10], col = "tan", las = 2)
```

Top 10 common words in positive reviews of American Airlines 

```{r}
frequency <- freq_terms(
  aa_pos,
  top = 10,
  at.least = 5,
  stopwords = "Top500Words"
)

# Make a frequency barchart
plot(frequency, las = 2)
```

Top 10 common words in positive reviews of China Southern 

```{r}
# Create frequency
frequency <- freq_terms(
  csa$titles, 
  top = 10, 
  at.least = 3, # At least 3 letters per term.
  stopwords = "Top200Words"
)

# Make a frequency barchart
plot(frequency, col = "tan", las = 2)

```

Good news! China Southern mostly receives positive words from customers review titles!!!

```{r}
# Word association
luft_titles <- lufthansa$titles
word_associate(luft_titles, match.string = "experience", 
               stopwords = c(Top200Words), text.unit = "sentence", wordcloud = TRUE,
               network.plot = TRUE, cloud.colors = c("gray85", "darkred"))

# Add title
title(main = "Lufthansa Reviews Associations")
```

Asscosiate words with "experience" term from Lufthansa customer reviews did not turn out so good!

We will create a comparison cloud for reviews of Lufthansa

```{r}
pos_aa <- paste(aa_pos, collapse = " ")
neg_aa <- paste(aa_neg, collapse = " ")
pos_luft <- paste(luft_pos, collapse = " ")
neg_luft <- paste(luft_neg, collapse = " ")
pos_csa <- paste(csa_pos, collapse = " ")
neg_csa <- paste(csa_neg, collapse = " ")

all_aa <- c(pos_aa, neg_aa)
all_luft <- c(pos_aa, neg_aa)
all_csa <- c(pos_csa, neg_csa)

all_aa_corp <- VCorpus(VectorSource(all_aa))
all_luft_corp <- VCorpus(VectorSource(all_luft))
all_csa_corp <- VCorpus(VectorSource(all_csa))

```


<<<<<<< HEAD
Create a dendrogram

```{r}


```


=======
>>>>>>> e53766ff904bcd1144eba0c2e2a2f470be8004e4
```{r}
all_luft_corp_clean <- tm_clean(all_luft_corp)

all_luft_tdm <- TermDocumentMatrix(all_luft_corp_clean)

all_luft_m <- as.matrix(all_luft_tdm)

# A comparison cloud
comparison.cloud(all_luft_m, max.words = 50, colors = c("#2196f3", "#F44336"))
```

Lufthansa vs China Southern Airlines Negative Reviews

```{r}
csa_luft_neg <- c(neg_luft, neg_csa)

csa_luft_neg_clean <- qdap_clean(csa_luft_neg)

csa_luft_neg_corp <- VCorpus(VectorSource(csa_luft_neg_clean))
csa_luft_neg_corp_tm <- tm_clean(csa_luft_neg_corp)

library(RWeka)
tokenizer <- function(x) {
  NGramTokenizer(x, Weka_control(min = 2, max = 3))
}

csa_luft_neg_tdm <- TermDocumentMatrix(csa_luft_neg_corp_tm, control=list(tokenize=tokenizer))
colnames(csa_luft_neg_tdm) <- c("LuftNegative", "ChinaSouthernNegative")
csa_luft_m <- as.matrix(csa_luft_neg_tdm)

library(dplyr)
csa_luft_df_neg <- csa_luft_m %>%
  # Convert to data frame
  as_data_frame(rownames = "word")
csa_luft_df_neg
```


```{r}
library(dplyr)
# Filter to words in common and create an absolute diff column
common_words <- csa_luft_df_neg %>% 
  filter(
    LuftNegative != 0,
    ChinaSouthernNegative != 0
  ) %>%
  mutate(diff = abs(LuftNegative - ChinaSouthernNegative))

# Extract top 10 common bigrams
(top10_df <- top_n(common_words, 10, diff))
```

Apyramid plot for negative words in reviews of Lufthansa and China Southern

```{r}
# Create the pyramid plot
library(plotrix)
pyramid.plot(top10_df$LuftNegative, top10_df$ChinaSouthernNegative, 
             labels = top10_df$word, gap = 4,
             top.labels = c("Lufthansa", "Words", "China Southern"), 
             main = "Negative Words in Common", unit = NULL)
```

Lufthansa seems to get more negative reviews on customer service and business class. Meanwhie, China Southern receives more complaints on delayed flights. 



